### 2023-04-05 chapter1/chapter1.tex
Clarified inference of species trees

\subsection{Inference of species trees}
The orthology inference pipeline was first repeated with the outgroup species \textit{Scaptodrosophila lebanonensis}. Orthologous groups with one sequence for each species were aligned, and 100 meta-alignments were constructed by randomly sampling 10,000 columns from these 9,435 alignments. (The alignments were not refined before sampling.) To determine the effect of invariant columns and gaps, two sampling strategies were used where invariant columns were allowed or disallowed and the maximum fraction of gaps was set at 0, 50, and 100\%. Their combination yielded six different sets of meta-alignments. A tree was fit to each meta-alignment with the LG substitution model and four discrete gamma rate categories using IQ-TREE 1.6.12~\cite{Nguyen2014, Le2008, Yang1994}. If the sampling strategy allowed invariant columns, an invariant rate category was included. The resulting trees from each set were merged into a majority consensus tree (Fig.~\ref{sfig:trees_LG}).

>>>>

\subsection{Inference of species trees}
The orthology inference pipeline was first repeated with the outgroup species \textit{Scaptodrosophila lebanonensis}. Orthologous groups with one sequence for each species were aligned, and 100 meta-alignments were constructed by randomly sampling 10,000 columns from these 9,435 alignments. (The alignments were not refined before sampling.) To determine the effect of invariant columns and gaps, two sampling strategies were used where invariant columns were allowed or disallowed and the maximum fraction of gaps was set at 0, 50, and 100\%. Their combination yielded six different sets of meta-alignments. A tree was fit to each meta-alignment with the LG substitution model, four discrete gamma rate categories, and optimized state frequencies using IQ-TREE 1.6.12~\cite{Nguyen2014, Le2008, Yang1994}. If the sampling strategy allowed invariant columns, an invariant rate category was included. The resulting trees from each set were merged into a majority consensus tree (Fig.~\ref{sfig:trees_LG}). All figures are derived from the maximum 50\% gap fraction meta-alignment set unless otherwise noted.
